\section{Architecture Requirements}
\subsection{Access Channel Requirements}
Any and all interactions by the user will be done through the Willburg Application.
\subsection{Quality Requirements}
\subsubsection{Performance}
\begin{enumerate}
	\item Images should only be captured and processed if some movement is detected to ensure that the server does not get overloaded.
	\item Images which are processed should not be large in size so they may be processed faster by the server.
	\item The system must be created with the most minimal and efficient coding
	practices possible, given that the result must still be reliable and robust.
\end{enumerate}
\subsubsection{Reliability}
\begin{enumerate}
	\item The system must be thoroughly tested on the server side, to
	ensure it will not cause faults or problems. 
	\item The notification warning users will receive must be sent out immediately after the image has been processed in a real-time manner.
\end{enumerate}
\subsubsection{Scalability}
\begin{enumerate}
	\item Modular programming should be used in order to ensure that there are no restrictions in terms of the systems ability to be extended and improved upon at later stages.
	\item The server should be able to process multiple images at once to ensure the real-time restriction is met.
\end{enumerate}
\subsubsection{Security}
\begin{enumerate}
	\item Depending on the technology being used the various security measures should be in place to ensure the integrity of the server, such as: SQL injections etc.
\end{enumerate}
\subsubsection{Flexibility}
\begin{enumerate}
	\item The system should be able to perform correctly even while under strain due to bulk processing without any loss of data.
	\item The system should be modularized to ensure both easy testing of components as well as addition of components without affecting the system.
\end{enumerate}
\subsubsection{Maintainability}
\begin{enumerate}
	\item The system should be designed in technologies which offer user support and continuous updates for extra functionality.
	\item The system must be well structured and documented to ensure future developers are able to understand and maintain the system.
	\item The modular design of the system must be such that if changes must be made to a part of the system, only that part itself should be changed.
\end{enumerate}
\subsubsection{Auditability}
\begin{enumerate}
	\item All images processed should be logged and traceable(user, date, time etc.) once pushed into the database.
\end{enumerate}
\subsubsection{Integrability}
\begin{enumerate}
	\item The system should be designed in a manner which allows for easy 
\end{enumerate}
\subsubsection{Cost}
\begin{enumerate}
	\item The tools used to design the system should, as far as possible be open source, free and not require a license.
	\item In certain cases, paid and licensed software may be suitable for specific aspects of the system. 
\end{enumerate}
\subsubsection{Usability}
\begin{enumerate}
	\item The Willburg application should be easy for users to interact with regarding the notifications they will be receiving.
\end{enumerate}